### 2021-10-28 tikz/bayes-rdm.tex
a major reorganization is underway, this is just an intermediate saved point

\usepackage{physics}

\usepackage{xcolor}
\definecolor{TurquoiseGreen}{HTML}{B8D5B8}
\definecolor{TealBlue}{HTML}{598392}
\definecolor{YellowOrange}{HTML}{FFB140}
\definecolor{RichBlack}{HTML}{011627}

@@

\tikzstyle{function} = [circle, draw, fill=TurquoiseGreen, text=RichBlack, text width=5.5em, text centered]
\tikzstyle{block} = [rectangle, draw, fill=TurquoiseGreen, text=RichBlack, minimum width=6em, text centered,  minimum height=4em, align=center]
\tikzstyle{derived} = [rectangle, draw, rounded corners, fill=YellowOrange!33, text=RichBlack, minimum width=6em, text centered,  minimum height=4em, align=center]
\tikzstyle{check} = [text=TealBlue, align=center]

\tikzstyle{line} = [draw, very thick, color=RichBlack, ->]
\tikzset{>=latex}

@@

    \node [block] (decision) at (4, 3) {Candidate decisions\\{\color{TealBlue}$\qty{x_1, x_2, \ldots, x_I}$}};
    \node [block] at (-4, 3) (scenarios) {Many possible futures\\{\color{TealBlue}$\qty{s_1, \ldots, s_J} \in \Omega$}};
    \node [function] (model) at (0, 0) {Deterministic system model\\{\color{TealBlue}$f(x, s)$}};
    \node [derived] at (0, -3) (smetrics) {Scenario metrics\\{\color{TealBlue}$u_{ij} = f(x_i, s_j)$}};
    \node [block] (prior) at (-4, -6) {Prior over scenarios\\{\color{TealBlue}$p(s)$}};\
    \node [derived] (weights) at (0, -6) {Scenario weights\\{\color{TealBlue}eq.~XX}};
    \node [derived] (combined) at (4, -6) {Distribution over\\outcomes\\{\color{TealBlue}$\hat{p}(u | x_i)$}};
    \node [derived] (dmetrics) at (8, -6) {Decision metrics\\{\color{TealBlue}$\hat{m}(x_i)$}};

@@

    \node [check] at (-9, 3) (span) {Do scenarios span\\plausible outcomes?};
    \path [line, dashed] (scenarios) -- (span);
    \node [check] at (9, 3) (represented) {Are relevant levers\\represented?};
    \path [line, dashed] (decision) -- (represented);
    \node [check] at (5, 0) (interpretable) {Is the model credible?\\Interpretable?};
    \path [line, dashed] (model) -- (interpretable);
    \node [check] at (5, -3) (discovery) {What are relevant regions\\of the $\qty(s, x)$ space?};
    \path [line, dashed] (smetrics) -- (discovery);
    \node [check] at (-4, -8) (priorcheck) {Are these consistent\\with prior knowledge?};
    \path [line, dashed] (prior) -- (priorcheck);
    \node [check] at (0, -8) (weightcheck) {Are computational\\issues apparent?};
    \path [line, dashed] (weights) -- (weightcheck);
    \node [check] at (4, -8) (ppc) {Are these consistent\\with our expectations?};
    \path [line, dashed] (combined) -- (ppc);

>>>>

\usepackage{physics}
\usepackage{libertine}

\usepackage{xcolor}
% FORZA GRANDE ROMA!!! https://teamcolorcodes.com/a-s-roma-color-codes/
\definecolor{giallo}{HTML}{F0BC42}
\definecolor{rosso}{HTML}{8E1F2F}
\definecolor{grigio}{HTML}{CACACC}
\definecolor{nero}{HTML}{000000}
\definecolor{thirds}{HTML}{31467A}

@@

\tikzstyle{function} = [circle, draw, fill=grigio, text=rosso, text width=5.5em, text centered]
\tikzstyle{block} = [rectangle, draw, fill=giallo, text=nero, minimum width=6em, text centered,  minimum height=4em, align=center]
\tikzstyle{derived} = [rectangle, draw, rounded corners, fill=rosso, text=grigio, minimum width=6em, text centered,  minimum height=4em, align=center]
\tikzstyle{check} = [text=thirds, align=center]

\tikzstyle{line} = [draw, very thick, color=nero, ->]
\tikzset{>=latex}

@@

    \node [block] (decision) at (4, 3) {Candidate decisions\\{$\qty{x_1, x_2, \ldots, x_I} \in \mathcal{X}$}};
    \node [block] at (-4, 3) (scenarios) {Many possible futures\\{$\qty{s_1, \ldots, s_J} \in \Omega$}};
    \node [function] (model) at (0, 0) {System model\\{$f(x, s)$}};
    \node [derived] at (0, -3) (smetrics) {Outcomes\\{$u_{ij} = f(x_i, s_j)$}};
    \node [block] (prior) at (-4, -6) {Prior over scenarios\\and model structures\\{$p(s)$}};\
    \node [derived] (weights) at (0, -6) {Scenario weights\\{eq.~XX}};
    \node [derived] (combined) at (4, -6) {Distribution over\\outcomes\\{$\hat{p}(u | x_i)$}};
    \node [derived] (dmetrics) at (8, -6) {Metrics and\\tradeoffs\\{$\hat{m}(x_i)$}};

@@

    \node [check] at (-9, 3) (span) {Do scenarios span\\plausible outcomes?};
    \path [line, dashed] (scenarios) -- (span);
    \node [check] at (9, 3) (represented) {Are relevant levers\\represented?};
    \path [line, dashed] (decision) -- (represented);
    \node [check] at (9, 0) (interpretable) {Is the model credible?\\Interpretable?};
    \path [line, dashed] (model) -- (interpretable);
    \node [check] at (9, -3) (discovery) {What are relevant regions\\of the $\qty(\Omega, \mathcal{X})$ space?};
    \path [line, dashed] (smetrics) -- (discovery);
    \node [check] at (-4, -8) (priorcheck) {Are these consistent\\with prior knowledge?};
    \path [line, dashed] (prior) -- (priorcheck);
    \node [check] at (0, -8) (weightcheck) {Are computational\\issues apparent?};
    \path [line, dashed] (weights) -- (weightcheck);
    \node [check] at (4, -8) (ppc) {Are these consistent\\with our expectations?};
    \path [line, dashed] (combined) -- (ppc);
